---
title: "DATA 555 Interactive Widgets"
author: "Megan Louttit"
date: "2025-04-25"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, make-data-clean}
here::i_am("Interactive Widgets .Rmd")

library(dplyr)
library(labelled)
library(gtsummary)
library(broom)
library(DT)
library(plotly)
library(htmltools)

# Load data
data_for_table <- readRDS(here::here("data", "simulated_data_for_table.RDS"))
communityattendancelevel <- read.csv(here::here("data","community_attendance_DATA550.csv"))

# Label variables
var_label(data_for_table) <- list(
  ParticipantID = "ID",
  Job = "Job",
  Interest_Level = "Personal Interest Level in Program",
  F_attendance = "Attended at Least 50% of Sessions"
)
```

Father Attendance Trends
=====================================  

Column
----------------------------------------------------------------

```{r, line-graph, fig.align='center', message = FALSE}
fig <- plot_ly(communityattendancelevel, x = ~Session_No.) %>%
  add_lines(y = ~Iponyabugali, name = "Iponyabugali", line = list(width = 2),
            hovertemplate = "<b>Session Number:</b> %{x}<br><b>Community:</b> Iponyabugali<br>%{y} men<extra></extra>") %>%
  add_lines(y = ~Igumamoyo, name = "Igumamoyo", line = list(width = 2),
            hovertemplate = "<b>Session Number:</b> %{x}<br><b>Community:</b> Igumamoyo<br>%{y} men<extra></extra>") %>%
  add_lines(y = ~Nyamwilolelwa, name = "Nyamwilolelwa", line = list(width = 2),
            hovertemplate = "<b>Session Number:</b> %{x}<br><b>Community:</b> Nyamwilolelwa<br>%{y} men<extra></extra>") %>%
  add_lines(y = ~Kisundi, name = "Kisundi", line = list(width = 2),
            hovertemplate = "<b>Session Number:</b> %{x}<br><b>Community:</b> Kisundi<br>%{y} men<extra></extra>") %>%
  add_lines(y = ~Kabangaja, name = "Kabangaja", line = list(width = 2),
            hovertemplate = "<b>Session Number:</b> %{x}<br><b>Community:</b> Kabangaja<br>%{y} men<extra></extra>") %>%
  add_lines(y = ~Buganda, name = "Buganda", line = list(width = 2),
            hovertemplate = "<b>Session Number:</b> %{x}<br><b>Community:</b> Buganda<br>%{y} men<extra></extra>") %>%
  layout(
    title = "Number of Fathers at Each Educational Session in Each Community",
    xaxis = list(title = "Session Number (1-15)"),
    yaxis = list(title = "Number of Fathers at Each Session (0-10)", fixedrange = TRUE),
    hovermode = "x unified"
  )

htmltools::browsable(
  div(style = "text-align: center;", fig)
)

```
<p style="font-size: 20px;">The above figure shows the number of fathers that attended each educational session by community. The figure shows that all communities had between 6 and 9 fathers present at the first session and that attendance rates varied greatly as the program continued. The highest session attendance was 10 fathers, while the lowest attendance was 0.</p>


Attendance by Job Type and Interest Level
=====================================  
Column
-------------------------------------

```{r, logistic-regression-job-unadjusted}
# Logistic models
logistic_model_job <- glm(F_attendance ~ Job, family = binomial, data = data_for_table)
logistic_model_interest <- glm(F_attendance ~ Interest_Level, family = binomial, data = data_for_table)

# Tidy & merge
logistic_table_job <- tidy(logistic_model_job) %>% mutate(Variable = "Job Type")
logistic_table_interest <- tidy(logistic_model_interest) %>% mutate(Variable = "Interest Level")

combined_table <- bind_rows(logistic_table_job, logistic_table_interest) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    Term = gsub("JobEntrepreneur", "Entrepreneur", term),
    Term = gsub("JobArchitect", "Architect", Term),
    Term = gsub("JobFarmer", "Farmer", Term),
    Term = gsub("JobFisherman", "Fisherman", Term),
    Term = gsub("JobSmall business", "Small Business", Term),
    Term = gsub("Interest_LevelNeutral", "Neutral Interest", Term),
    Term = gsub("Interest_LevelVery interested", "Very Interested", Term),
    Coefficient = round(estimate, 2),
    `Standard Error` = round(std.error, 2),
    `Z-Statistic` = round(statistic, 2),
    `P-Value` = round(p.value, 3)
  ) %>%
  select(Variable, Term, Coefficient, `Standard Error`, `Z-Statistic`, `P-Value`)

# Render the table with explicit settings for alignment and column width
datatable(combined_table,
          options = list(
            pageLength = 15,  # Number of rows to display initially
            scrollX = TRUE,
            scrollY = '400px',  # Fixed height for the table
            autoWidth = FALSE,  # Disable autoWidth for more control over column width
            dom = 'Bfrtip',
            buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
            columnDefs = list(
              list(className = 'dt-center', targets = c(0, 1)),  # Center 'Variable' and 'Term' columns
              list(className = 'dt-right', targets = c(2, 3, 4, 5)),  # Right-align numeric columns
              list(width = '200px', targets = c(0, 1)),  # Set width for 'Variable' and 'Term' columns
              list(width = '150px', targets = c(2, 3, 4, 5)),  # Set width for numeric columns
              list(orderable = FALSE, targets = 0)  # Make 'Variable' column non-sortable if desired
            )
          ),
          extensions = 'Buttons',
          rownames = FALSE,
          caption = htmltools::tags$caption(
            style = 'caption-side: top; text-align: left; font-weight: bold; font-size: 16px; color: black;',
            'Logistic Regression Model of Attendance by Job Type and Interest Level'
          )) %>%
  # Apply consistent CSS for both header and body
  formatStyle(columns = 1:6,
              padding = '5px') %>%
  htmlwidgets::onRender("
    function(el, x) {
      // Custom CSS for aligning the header and body
      $('th').css({
        'text-align': 'center',  // Center-align header text
        'padding': '10px',  // Set padding for header cells
        'border': '1px solid #ddd'  // Set border for header cells
      });
      $('td').css({
        'text-align': 'center',  // Center-align data cells
        'padding': '10px',  // Set padding for data cells
        'border': '1px solid #ddd'  // Set border for data cells
      });
      $('table').css('border-collapse', 'collapse');  // Ensure no extra spacing between cells
    }
  ")
```
<p style="font-size: 20px;">Table 1 shows the results of fitting a logistic regression model of fathers' attendance by two different variables: the type of job they work and their interest level in the program at baseline. The data shows that none of the variables are statistically significantly associated with attendance at educational sessions. All job types and interest levels had a p-value greater than 0.05 when compared to their respective intercepts (job type had an intercept of "other", interest level had an intercept of "interested").</p>


About
=====================================  
Column {data-width=250 .tabset .tabset-fade}
-----------------------------------------------------
<p style="font-size: 20px;">Project Purpose:
This project analyzed attendance trends of fathers in a parenting program designed to improve early childhood development outcomes in Mwanza, Tanzania. This project aimed to answer the following questions:
1. What factors predict (or are associated with) fathers’ attendance at early childhood development educational sessions?
2. How did father attendance rates change over time in different communities?</p>

<p style="font-size: 20px;">Dataset Description:
The data presented in this dashboard are confidential, as related publications are still in development. The data was collected from June to November 2024 from 62 fathers participating in a parenting program across six communities in Mwanza, Tanzania. Data sources include a baseline survey capturing sociodemographic information and attendance forms documenting father participation at each educational session (15 sessions total).</p>

<p style="font-size: 20px;">Real-World Impact:
This dashboard will be used to help inform the development of a future parenting program in Mwanza, Tanzania. Additionally, it is helpful in showing that the type of job fathers work and their baseline interest level in the program did not significantly impact their attendance at sessions, guiding future research.</p>

<p style="font-size: 20px;">Link to Repository:
The link to the GitHub Repository associated with this dashboard is: https://github.com/mloutti/DATA555_Final_Project</p>
